Test 11

### 2022-07-14 src/tex/ms.tex
delete title
Test
Update
Bump

\twocolumn[
\icmltitle{I deleted the title}

@@

\begin{abstract}
We present an automatic approach to discover analytic population models for gravitational-wave (GW) events from data.
As more gravitational-wave (GW) events are detected, flexible models such as Gaussian Mixture Models have become more important in fitting the distribution of GW properties due to their expressivity.
However, flexible models come with many parameters that lack physical motivation, making interpreting the implication of these models challenging.
In this work, we demonstrate symbolic regression can complement flexible models by distilling the posterior predictive distribution of such flexible models into interpretable analytic expressions.
We recover common GW population models such as a power-law-plus-Gaussian, and find a new empirical population model which combines accuracy and simplicity.
This demonstrates a strategy to automatically discover interpretable population models in the ever-growing GW catalog, which can potentially be applied to other astrophysical phenomena.
\end{abstract}

@@

First, we implement limits on which operators can be nested, and how deeply.
We impose the following nested constraints:
\begin{enumerate}
    \item No operator with arity of 1 (i.e., an operator taking a single argument) may be nested with another arity-1 operator, unless the operator is square.
    \begin{enumerate}
        \item However, we permit a square to be nested inside itself once, as such a combination may be used to make a quadratic operation with few operations.
    \end{enumerate}
    \item The division operator may only be nested inside itself once.
    \item The power operator may not contain any arity-1 operator.
\end{enumerate}
We also impose the following constraints on maximum complexity within each operator:
\begin{enumerate}
    \item The power operator may only have a maximum complexity of 9 in its base, and 3 in its exponent.
    \item The division operator may have any complexity in the numerator, but a maximum complexity of 7 in the denominator.
    \item The Gauss operator may only have a maximum complexity of 11 in its argument.
    \item The conditional operator may only have a maximum complexity of 5 in its condition, and 11 in its resultant argument.
\end{enumerate}
These prevent \pysr from finding expressions which, despite being low-complexity and high-accuracy, are still uninterpretable to a human scientist due to unusual combinations of operators compared to typical expressions found throughout physics and astrophysics.

>>>>

\twocolumn[
\icmltitle{Test 11}

@@

\begin{abstract}
Test11. We present an automatic approach to discover analytic population models for gravitational-wave (GW) events from data.
As more gravitational-wave (GW) events are detected, flexible models such as Gaussian Mixture Models have become more important in fitting the distribution of GW properties due to their expressivity.
However, flexible models come with many parameters that lack physical motivation, making interpreting the implication of these models challenging.
In this work, we demonstrate symbolic regression can complement flexible models by distilling the posterior predictive distribution of such flexible models into interpretable analytic expressions.
We recover common GW population models such as a power-law-plus-Gaussian, and find a new empirical population model which combines accuracy and simplicity.
This demonstrates a strategy to automatically discover interpretable population models in the ever-growing GW catalog, which can potentially be applied to other astrophysical phenomena.
\end{abstract}

@@

First, we implement limits on which operators can be nested, and how deeply.
We impose the following nested constraints:
\begin{enumerate}
    \item No operator with arity of 1 (i.e., an operator taking a single argument) may be nested with another arity-1 operator, unless the operator is square.
    \begin{enumerate}
        \item However, we permit a square to be nested inside itself once, as such a combination may be used to make a quadratic operation with few operations.
    \end{enumerate}
    \item The division operator may only be nested inside itself once.
    \item The power operator may not contain any arity-1 operator.
\end{enumerate}
We also impose the following constraints on maximum complexity within each operator:
\begin{enumerate}
    \item The power operator may only have a maximum complexity of 9 in its base, and 3 in its exponent.
    \item The division operator may have any complexity in the numerator, but a maximum complexity of 7 in the denominator.
    \item The Gauss operator may only have a maximum complexity of 11 in its argument.
    \item The conditional operator may only have a maximum complexity of 5 in its condition, and 11 in its resultant argument.
\end{enumerate}
These prevent \pysr from finding expressions which, despite being low-complexity and high-accuracy, are still uninterpretable to a human scientist due to unusual combinations of operators compared to typical expressions found throughout Test?
